---
title: "R Code Examples"
author: "Derek Chiu"
date: '2019-05-23'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#>")
```

# Example Data

A toy dataset is constructed below. We simulate 10 variables across 100 observations, creating various data types such as: integer, double, factor, ordered factor, logical, date, and character.

```{r toy-data}
# Set number of cases and random seed
library(magrittr)
n_cases <- 100
set.seed(1)

# Toy data with various data types
toy_data <- tibble::tibble(
  patient_id = seq_len(n_cases),
  age = rnorm(n = n_cases, mean = 55, sd = 5),
  bmi = rnorm(n = n_cases, mean = 23, sd = 2),
  date_dx = sample(seq(as.Date("2000-01-01"), as.Date("2010-12-31"), by = "day"), n_cases),
  stage = factor(sample(c("I", "II", "III", "IV"), size = n_cases, replace = TRUE)),
  grade = factor(sample(1:3, size = n_cases, replace = TRUE)),
  nodes = rbinom(n = n_cases, size = 5, prob = 0.2),
  feel = sample(forcats::fct_inorder(
    c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"),
    ordered = TRUE), size = n_cases, replace = TRUE),
  alive = sample(c(TRUE, FALSE), size = n_cases, replace = TRUE),
  comment = sample(stringr::words, size = n_cases)
)

toy_data
```

# Filters

Use `==` to filter for equalities.

```{r}
toy_data %>%
  dplyr::filter(grade == 1)
```

Use `&` or `,` to separate additional conditions.

```{r}
toy_data %>%
  dplyr::filter(grade == 1, stage == "II")
```

```{r}
toy_data %>%
  dplyr::filter(grade == 1 & stage == "II")
```

Pipe to `nrow()` to get number of cases.

```{r}
toy_data %>%
  dplyr::filter(grade == 1, stage == "II") %>% 
  nrow()
```

We can use inequalities for numeric variables (type `dbl`).

```{r}
toy_data %>% 
  dplyr::filter(age < 50, bmi >= 20)
```

# Counts

We can tabulate counts for every level of a factor.

```{r}
toy_data %>% 
  dplyr::count(feel)
```

Bivariate counts also work.

```{r}
toy_data %>% 
  dplyr::count(feel, stage)
```
